---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(nycflights13)
```


## Easy

### Exercise 1

First add arr_time and dep_time. Rename it as delay. Find mean delay and remove NAs from the delay using na.rm.


```{r q, exercise=TRUE}

```

```{r q-hint}
summarise(mean_delay = mean(delay,na.rm = TRUE))
```


## Intermediate

### Exercise 2

Find the mean delay of flights given that arr_delay > 30 minutes and find the carrier with the highest delay.


```{r print-limit, exercise=TRUE, exercise.eval=TRUE}

```

```{r print-limit-hint}
flights %>%
	filter(arr_delay > 30) %>%
	group_by(carrier) %>%
	summarise(mean_delay = mean(arr_delay)) %>%
  arrange(desc(mean_delay))
```

## Challenging

### Exercise 3

Using flights data, group data by carrier and summarize the data by arr_delay. Finally, plot the summary statistics.

```{r summary_stats, exercise=TRUE, exercise.eval=TRUE}
flights
```

```{r summary_stats-hint, exercise=TRUE, exercise.eval=TRUE}
flights %>% group_by(carrier) %>% summarise(mean_ardelay = mean(arr_delay,na.rm = TRUE)) %>% ggplot(aes(x=carrier, y = mean_ardelay, fill = carrier)) + geom_bar(stat = "identity") + theme_classic()
```
