---
title: "Exercise 5.5.2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Easy

### Question 1 

```{r quiz}
quiz(
  question(" ________ add new variables/columns to the existing dataset or transform existing variables.",
    answer("transmute"),
    answer("add"),
    answer("mutate", correct = TRUE),
    answer("arrange")
  )
)
```

### Question 2
Let's make a new variable called speed using the mutate function.
```{r ,exercise=TRUE, exercise.eval=TRUE}

```

## Intermediate

### Question 3

Question is in parts.
Part 1: Filter the Delta flights ("DL") for the month November and December.
Part 2: Assign it a new variable name.
Part 3: Find how many hours and minutes was the air time.

```{r ranking, exercise=TRUE, exercise.eval=TRUE}
library(tidyverse)
library(nycflights13)
flights

```

```{r ranking-hint}
filtered_data <- filter(flights, month %in% c(11, 12) & carrier == "DL")
transmute(flights,
  air_time,
  hour = air_time %/% 60,
  minute = air_time - hour*60
)
```

### Question 4

Find the lag, lead values, rank in descending order of the following: (1) c(800,340,67,1888,98,0)
```{r arrange, exercise=TRUE, exercise.eval=TRUE}


```



## Challenging

### Question 5

Find the 5 shortest distance travelled and 5 shortest time taken.

```{r question, exercise=TRUE, exercise.eval=TRUE}
flights

```