---
title: "Learnr_3.3.1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```


## Easy

### Exercise 1

Write the R code for putting mpg dataset into a mpg dataframe

```{r 1, exercise=TRUE, exercise.eval=TRUE}
mpg<- data.frame(mpg)
```

### Exercise 2  

Write the R code for Viewing the mpg dataframe
```{r 2, exercise=TRUE, exercise.eval=TRUE}
View(mpg)
```

##  Intermediate Level

### Exercise 3

Modify the following code to map the shapes of points to drv variable 
```{r 3, exercise=TRUE, exercise.eval=TRUE}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape= drv))
```

### Exercise 4

Quiz

```{r quiz}
quiz(
  question("Which of the following are considered asethetics in geom_point ?",
    answer("fill", correct = TRUE),
    answer("shape", correct = TRUE),
    answer("size", correct= TRUE),
    answer("length")
  )
)
```

## Advanced

### Exercise 5

Divide mpg dataframe into 2 half and plot 2 separate geom_point graphs respectively with displ on x-axis and hwy on y-axis  

```{r 5, exercise=TRUE, exercise.eval=TRUE}
half_size <- floor(0.5*nrow(mpg))
set.seed(123123)
mpg_half <- sample(seq_len(nrow(mpg)),size= half_size)

mpg_1 <- mpg[mpg_half, ]
mpg_2 <- mpg[-mpg_half, ]
ggplot(data= mpg_1) +
  geom_point(mapping = aes(x= displ, y = hwy))
ggplot(data=mpg_2) +
  geom_point(mapping = aes(x= displ, y = hwy))
```
