---
title: "5.4.1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Easy 

### Question 1 (Quiz type)

*we will be using the nycflights database in these exercises*

```{r quiz}
quiz(
  question(" The ______ operator allows you to string operations in a left-to-right fashion.",
    answer("This %<%"),
    answer("This %%%"),
    answer("This %>%", correct = TRUE),
    answer("This >%>%")
  )
)
```

```{r quiz2}
quiz(
  question(" Which of the following return a subset of the columns of a data frame?",
    answer("get"),
    answer("select", correct = TRUE),
    answer("set"),
    answer("retrieve")
  )
)
```


## Intermediate

### Question 2

*These questions will be in parts *
Part1: Make a new variable called delay which will be the total delay from departure to arrival.
Part2: Since we donot want some variables like arr_time, dep_time etc., let's drop it.

```{r flights, exercise=TRUE, exercise.eval=TRUE}
?flights

```

```{r flights-hint}
library(tidyverse)
library(nycflights13)
flights$delay <- flights$arr_delay + flights$dep_delay
select(flights, -c(arr_delay,dep_delay))
```

## Challenging

### Question 3

Let's remove all the time variables. Can we use any_of to do the same?

```{r Remove, exercise=TRUE, exercise.eval=TRUE}

```

```{r Remove-hint}
select(flights, -contains("time"))
```
