---
title: "5.2.4"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Easy 

### Question 1 

*we will be using the nycflights database in these exercises*

In the flights dataset, correct the following code so as to find the flights departed in March and April (why is it wrong?): 

```{r Correct_the_code, exercise=TRUE}
library(nycflights13)
library(tidyverse)
filter(flights, month == (3 |4 ))
```

```{r Correct_the_code-hint}
# Use infix or match operator (%in% or month == 3| month == 4)
```

## Intermediate

### Question 2

*These questions will be in parts *
Part1: Arrange flights in the order of year, month and day
Part2: Filter Delta flights departed in the month of November and December (carrier is DL)
How many rows are there now?

```{r flights, exercise=TRUE, exercise.eval=TRUE}
?flights

```

```{r flights-hint}
arrange(flights,year, month, day)
filter(flights, month %in% c(11, 12) & carrier == "DL")
nrow(filter(flights, month %in% c(11, 12) & carrier == "DL"))
```

## Challenging

### Question 3

Missing data in the flights dataset would suggest the flight being cancelled so we would prefer to remove those. Remove NAs rows from arr_delay and dep_delay.

```{r Remove_missing, exercise=TRUE, exercise.eval=TRUE}

```
