---
title: HW
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## ExercisesUpTo3.3.1

### question 1


write the code that will load tidyverse:

```{r two-plus-two, exercise=TRUE}

```

### question 2

if you want learn more about the variables in mpg which code should you run

```{r two-plus-three, exercise=TRUE}

```

### question 3

enter the code that creates a scatter plot

```{r two-plus-four, exercise=TRUE}

```

### question 4

enter the code that adds color to the class 

```{r two-plus-five, exercise=TRUE}

```

### question 5

run the code that adds size to the class.

```{r two-plus-six, exercise=TRUE}

```

## ExercisesUpTo3.6.1

### question 1

what is difference between facet_grid and facet_wrap

```{r two-plus-seven, exercise=TRUE}

```

### question 2

run a code with facet_grid in it

```{r two-plus-eight, exercise=TRUE}

```

### question 3

run a code with face_wrap in it.

```{r two-plus-nine, exercise=TRUE}

```

### question 4

run a code with geom_smooth in it

```{r two-plus-ten, exercise=TRUE}

```

### question 5

run a code with geom_piont in it

```{r two-plus-zero, exercise=TRUE}

```